---
title: "Capstone"
author: "Anupam Verma"
date: "1/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Setting Directory and Loading Required Libraries
```{r}
setwd("C:\\Users\\anupverma\\Desktop\\GLL-BABI\\Capstone\\Datasets")
#install.packages("jsonlite")
library(jsonlite)
library(dplyr)
library(ggplot2)
```


#Read Grocery and Gourmet Review Data
```{r}
reviewdata=stream_in(file("C:\\Users\\anupverma\\Desktop\\GLL-BABI\\Capstone\\Datasets\\Grocery_and_Gourmet_Food_5\\Grocery_and_Gourmet_Food_5.json"))

reviewdata_flat = flatten(reviewdata)
str (reviewdata_flat)
library(tibble)
reviewdata_tbl=as_data_frame(reviewdata_flat)
reviewdata_tbl
view(head(reviewdata_tbl))
```
#PART -2 Read Review Full Data
```{r}
#fullreviewdata=stream_in(file("C:\\Users\\anupverma\\Desktop\\GLL-BABI\\Capstone\\Datasets\\Full_Grocery_and_Gourmet\\Grocery_and_Gourmet_Food.json"))

#fullreviewdata_flat = flatten(fullreviewdata)
#str (fullreviewdata_flat)
#library(tibble)
#fullreviewdata_tbl=as_data_frame(fullreviewdata_flat)
#fullreviewdata_tbl
#view(head(fullreviewdata_tbl))
```

#Reading Metadata
```{r}
metadata=stream_in(file("C:\\Users\\anupverma\\Desktop\\GLL-BABI\\Capstone\\Datasets\\meta_Grocery_and_Gourmet_Food\\meta_Grocery_and_Gourmet_Food.json"))
metadata_flat = flatten(metadata)
str (metadata_flat)
library(tibble)
metadata_tbl=as_data_frame(metadata_flat)
metadata_tbl
view(head(metadata_tbl))
```

#Data Cleaning and EDA
#Converting the data type of 'Review_Time' column in the Dataframe 'dataset' to datetime format.
```{r}
month=substr(reviewdata_tbl$reviewTime,1,2)
month
date=substr(reviewdata_tbl$reviewTime,4,5)
date
date=gsub(",", "", date, fixed=TRUE)
year=substr(reviewdata_tbl$reviewTime,7,11)

library(stringr)
year=str_trim(year, side = c("both", "left", "right"))
newdate=paste(year,month,date,sep = "-")
newdate

newdate=as.Date(newdate,format="%Y-%m-%d")
str(newdate)
```
#Removing Unnecessary columns
```{r}
View(head(reviewdata_tbl))
reviewdata_tbl=reviewdata_tbl[-c(11:29)]

```
#Merging New Date field to Existing Dataframe

```{r}
reviewdata_tbl$newreviewtime=newdate
reviewdata_tbl$newyear=year
reviewdata_tbl$newmonth=month
reviewdata_tbl$newdate=date
```

#NUMBER OF REVIEWS OVER THE YEARS
#Grouping by year and taking the count of reviews for each year.
```{r}
yearly=reviewdata_tbl %>%select(newyear) %>% group_by(newyear) %>% summarise(count=n())
yearly=as.data.frame(yearly)
library(ggplot2)
ggplot(mapping=aes(x=yearly$newyear,y=yearly$count,group = 1))+geom_path()
#ggplot(data=yearly,aes(x=newyear,y=yearly$count))+geom_bar(data=yearly,stat = "count",position = "stack",stat_count("identity"))+geom_text(stat='count', aes(mapping=yearly$count), vjust=-1)

head(yearly)
```
#NUMBER OF REVIEWS BY MONTH
#Grouping on Month and getting the count
```{r}
monthly=reviewdata_tbl %>%select(newmonth) %>% group_by(newmonth) %>% summarise(count=n())
monthly=as.data.frame(monthly)
monthly
library(ggplot2)
ggplot(mapping=aes(x=monthly$newmonth,y=monthly$count,group=1))+geom_path()
```
#DISTRIBUTION OF OVERALL RATING FOR 'Grocery and Gourmet' CATEGORY REVIEWS ON AMAZON

```{r}
overall_rating=reviewdata_tbl %>%select(overall) %>% group_by(overall) %>% summarise(count=n())
overall_rating=as.data.frame(overall_rating)
overall_rating

library(ggplot2)
ggplot(mapping=aes(x=overall_rating$overall,y=overall_rating$count,group=1))+geom_line()
#show Y as percentage
#barplot(height = overall_rating$count,x=overall_rating$overall,y=overall_rating$count)
ggplot(data = reviewdata_tbl, 
         aes(x = reviewdata_tbl$overall)) + 
    geom_histogram(aes(y = ..count../sum(as.numeric(..count..))*100),binwidth = 1)

```
#AVERAGE OVERALL RATINGS OVER THE YEARS
```{r}
Yearly_Avg_Rating=summarise(group_by(reviewdata_tbl$overall,reviewdata_tbl$NewYear_Fac),m=mean(reviewdata_tbl$overall))

group_by(reviewdata_tbl$overall)

reviewdata_tbl$NewYear_Fac=as.factor(reviewdata_tbl$newyear)
?barplot()

str(reviewdata_tbl)
Yearly_Avg_Rating
```



